---
title: "Tutorial: R for Data Science"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(ggplot2)
knitr::opts_chunk$set(echo = FALSE)
```

## Info

References:  
[R for data sciecne book](https://r4ds.had.co.nz)  
[Excercsie solutions](https://jrnold.github.io/r4ds-exercise-solutions/index.html)

## Workflow
From [Chapter 6](https://r4ds.had.co.nz/workflow-scripts.html)  
6.1 Running codes:  
You can create a new script in RStudio: **File --> New File --> R Script**  
Useful shorcuts:  
**`Cmd/Ctrl+Enter`** for running current line of codes. After running it, it will automatically move your cursor to the next code chunks.  
**`Cmd/Ctrl+Shift+S`** for execute the complete script.

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Exploratory Data Analysis (EDA)  
From [Chapter 7](https://r4ds.had.co.nz/exploratory-data-analysis.html)  
Exploratory Data Analysis (EDA) is a state of mind to develop an understanding of your data, and it is an interactive cycle:  
1.Generate questions about your data  
2.Search for answers by visualizing, transforming, and modeling your data.  
3.Use what you learn to refine your questions and/or generate new questions.  

### Exercise

First have a look at the `diamonds` dataset:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
# try to print first 5 rows
# try to see the summary statistcs of each column
diamonds
```

```{r print-limit-hint}
head(diamonds)
summary(diamonds)
```

```{r histo-price, exercise=TRUE, exercise.eval=TRUE}
# Visualize the distribution of price below 2500 using histogram
# hint: filter(), geom_histogram()
ggplot(data = filter(diamonds, price > 3000)) +
  geom_bar(
    mapping = aes(x=price),
    bins = 30, 
    center = 0
  )
```

```{r histo-price-hint}
ggplot(data = filter(diamonds, price < 2500)) +
  geom_histogram(
    mapping = aes(x=price),
    bins = 30, 
    center = 0
  )
```

### EDA frist step: Generate question  
Why there are no diamonds with a price of around $1500?
